---
title: "R Session for Chapter 02"
author: "Shun Zhu"
date: "Wednesday, March 04, 2015"
output: pdf_document
---


***

### Feathers

#### 1. Good at data analysis
#### 2. It is totally free
#### 3. Lots of built-in packages
#### 4. Beautiful graphics 

***

***
### 00. Load necessary packages

```{r}

# install.packages('ISLR')
library(ISLR)

```
***


***

### 01. Basic command

```{r}

# vectors, data, matrices, subsetting
x=c(2,7,5)
x
y=seq(from=4, length=3, by=3)
?seq
y
# vector operations in parallel 
x+y

# element-wise division
x/y
x^y

x[2]
x[2:3]

# Use '-' to remove elements
x[-2]

# Remove the collection of indices 1 and 2,
x[-c(1,2)]

# Matrix : two way array
z=matrix(seq(1,12),4,3)
z

# Subset matrix
z[3:4,2:3]
z[,2:3]

### When we took just the first column of z, that became a vector
z[,1]

### Use drop=FALSE to keep it as matrix
z[,1,drop=FALSE]

### Dimensions of the matrix.
dim(z)

### Tell you what you have available in your working directory.
ls()
### Use rm to clean up your working directory
rm(y)
ls()

```

***


***

### 02. Generate data and Simulation

```{r}

# Generating random data, graphics
?runif

# random uniform
x=runif(50)

# random Gaussion
y=rnorm(50)

plot(x,y)

```

***


***

### 03. Plotting
#### One doesn't think too much about the design of graphics, but a lot goes into it, such as aspect ratios, how much space to put around the points on a plot, between the edge of the points and the axes. Just things like spacing of the axes, how many ticks, and so on

```{r}

plot(x,y)
plot(x,y,xlab="Random Uniform",ylab="Random Normal",pch="*",col="blue")

### a panel of plots with two rows and one column.
par(mfrow=c(2,1))
plot(x,y)
hist(y)

###  reset it with another mfrow command.
par(mfrow=c(1,1))

```

***


***

### 04. Reading in data

```{r}

### Reading in data
### Auto is in the ISLR package

names(Auto)
dim(Auto)

### Data frame
###	It's sort of like a matrix, except that the columns can ###	be variables of different kinds. So you can have what ###	we call factors, and continuous variables, and 
###	matrices, and so on, which is really the way we think ###	of observations in statistics.

class(Auto)
 
summary(Auto)

### Data frame is also a list. getting the element of a list we can use $

plot(Auto$cylinders,Auto$mpg)
plot(Auto$cyl,Auto$mpg)

### attach creates a workspace with all the named variables as now variables in your workspace.So now you can access them by name.
attach(Auto)

### command Search, it tells us our various workspaces.
search()
plot(cylinders,mpg)
cylinders=as.factor(cylinders)
plot(cylinders,mpg,xlab="Cylinders",ylab="Mpg",col="red")
pdf(file="../mpg.pdf")
plot(cylinders,mpg,xlab="Cylinders",ylab="Mpg",col="red")
dev.off()
pairs(Auto,col="brown")
pairs(mpg~cylinders+acceleration+weight,Auto)

```

***

